---
title: "Websites"
subtitle: "OST-HS23: Open Science Tools <br> authoring and publishing workflows for collaborative scientific writing"
author: "Lars Schöbitz"
date: "2023-10-24"
date-format: long
footer: "[{{< fa link >}} ost-hs23.github.io/website/](https://ost-hs23.github.io/website/)"
logo: "../images/ghe-square-logo-vector.svg"
format:
  revealjs:
    theme: ../style/slides.scss
    transition: fade
    slide-number: true
    chalkboard: true
editor: source
execute:
  freeze: auto
  echo: true
---

```{r}
#| label: setup
#| include: false

# set width of code output
options(width = 65)

# load background packages
library(countdown)
```

# Anatomy of a Quarto project

## Quarto projects

-   Quarto projects have a `_quarto.yml` file

-   The `type` field in this file indicates the type of project:

    -   `default`: Collection of documents

    -   `website`: Websites (and blogs)

    -   `books`: Books 😃

## Quarto websites

-   Websites are essentially `format: html` + a Quarto Project

-   But a website is different than `format: html` in that it has multiple pages

-   Websites are our first exploration into Quarto Projects

-   Websites and books are very similar in that they associate multiple pages/resources into a connected resource

## Our turn

::: task
Let's build a website together from scratch. We will highlight the following feautures of Quarto websites:

-   `_quarto.yml`

-   `index.qmd` & `about.qmd` / landing page / change landing page

-   Navigation

-   Freeze

-   An aspect of the workshop webpage that you fancy?
:::

## Your turn

::: task
Pick up where we left off and

-   Add your details to the about page [about page](https://quarto.org/docs/websites/website-about.html).
:::

```{r}
#| echo: false

countdown(minutes = 10)
```

# Wrap up

## Learn more

::: learn-more
[quarto.org/docs/websites](https://quarto.org/docs/websites/)

```{=html}
<iframe src="https://quarto.org/docs/websites" width="100%" height="500" style="border:2px solid #123233;" title="Quarto Journal Articles"></iframe>
```
:::


